---
title: "p8105_hw1_ts3349"
author: "Tessa Senders"
date: "9/14/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

```{r problem 1 library}
library(tidyverse)
```

Create a dataframe as specified with four columns.
```{r problem 1 part 1}
prob_1_df <- tibble(
  col_1 = rnorm(10),
  col_2 = col_1 > 0,
  col_3 = c("Var 1", "Var 2", "Var 3", "Var 4", "Var 5", "Var 6", "Var 7", "Var 8", "Var 9", "Var 10"),
  col_4 = factor(c("level 1", "level 2", "level 3", "level 2", "level 1", "level 3", "level 1", "level 2", "level 2", "level 3"))

)

prob_1_df

mean(prob_1_df$col_1)
mean(prob_1_df$col_2)
mean(prob_1_df$col_3)
mean(prob_1_df$col_4)
```
R can take the mean of the numeric variable (col_1) and the logical variable (col_2).  R cannot take the mean of the character variable (col_3) and the mean of the factor variable (col_4).

```{r problem 1 part 2, eval=FALSE}
as.numeric(prob_1_df$col_2)
as.numeric(prob_1_df$col_3)
as.numeric(prob_1_df$col_4)
```
The logical variable is converted into 0s and 1s (0 for FALSE and 1 for TRUE).  The character variable is converted into NA values since a character value has no intrinsic numeric value.  The factor variable is converted into numeric values ranging from 1 to 3 since the factor has 3 levels.

It makes sense that the mean of the logical variable is the mean of the variable after being converted into a numeric variable (mean of 0s and 1s).  It makes sense you cannot find the mean of the character variable since all the character values are converted into NA values when converting from character to numeric.  A factor variable is not converted into a numeric variable when attempting to find the mean.  The mean of a factor variable can only be found if the variable is converted into a numeric variable first.  R can only find the mean of a numeric or logical variable and not character or factor variables.

convert the logical vector to numeric, and multiply the random sample by the result
convert the logical vector to a factor, and multiply the random sample by the result
convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
```{r problem 1 part 3}
as.numeric(prob_1_df$col_2) * prob_1_df$col_1

as.factor(prob_1_df$col_2) * prob_1_df$col_1

as.numeric(as.factor(prob_1_df$col_2)) * prob_1_df$col_1
```

# Problem 2

the data in this dataset, including names / values of important variables
the size of the dataset (using nrow and ncol)
the mean flipper length
```{r problem 2 part 1}
data("penguins", package = "palmerpenguins")
head(penguins)

nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```


Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).

Export your first scatterplot to your project directory using ggsave
```{r problem 2 part 2}

```



